---
title: "descriptiveanalysis"
format: html
editor: visual
echo: false
warning: false
toc: true
toc-depth: 4
---

```{r}
source('dataloading.R')

library(surveyexplorer)
```

# Descriptive Statistics

## Demographics

### Gender

```{r}
single_freq(oap, question = 'gender')


```

## Residence Status

```{r}
single_freq(oap, question = 'residence_status')

```

```{r}
single_table(oap, question = 'residence_status')

```

## Citizenship

*How many respondents plan to apply for citizenship*

```{r}

single_freq(oap, question = 'plan_to_apply')
```

*Citizenship aspirations by gender*

```{r}
surveyexplorer::single_table(oap, question = 'plan_to_apply', group_by = 'gender', subgroups_to_exclude = 'Keine Angabe / anonymisiert')

```

# Citizenship Applications

## Not yet applied for citizenship

```{r}
surveyexplorer::multi_freq(oap, question = starts_with('whynotapply'))

```

```{r}
surveyexplorer::multi_table(oap, question = starts_with('whynotapply'), na.rm = TRUE)
```

## Against applying for citizenship

```{r}
surveyexplorer::multi_freq(oap, question = starts_with('whyagainstapply'))

```

```{r}
surveyexplorer::multi_table(oap, question = starts_with('whyagainstapply'), na.rm = TRUE)
```

## Already applied 

```{r}
surveyexplorer::multi_freq(oap, question = starts_with('whyapply'))

```

```{r}
surveyexplorer::multi_table(oap, question = starts_with('whyapply'), na.rm = TRUE)
```

# Frequency of interactions with Bureaucracy

*Please indicate how frequently you have interacted with the following authorities*

```{r}
surveyexplorer::matrix_table(oap, question = starts_with('interaction')) 
```

# Experiences with Bureaucracy

*How would you rate the treatment you received when engaging with the following activities*

-   The employee treated me with dignity and respect

-   The employee treated me fairly 

-   The process and requirements were made clear to me

## Bamf

```{r}
surveyexplorer::matrix_table(oap, question = starts_with('bamf.'))

```

## Auslanderbehörde

```{r}
surveyexplorer::matrix_table(oap, question = starts_with('auslander.'))

```

## Job Center

```{r}
surveyexplorer::matrix_table(oap, question = starts_with('jobcenter.'))

```

# Overwhelmed

*With respect to the bureaucratic encounters you selected above, to what extent do you agree with the following statement: At times I was overwhelmed or unable to manage bureaucratic tasks* 

```{r}
surveyexplorer::matrix_table(oap, question = 'overwhelmed')

```
